---
title: "Data preparation including all gender categories"
author: "Anne Margit"
date: "04/25/2020"
output: github_document
---

> Final dataset including all gender categories

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=T, message=F}
library(ggplot2)
library(dplyr)
library(knitr)
library(arsenal)
library(tidyverse)
library(anytime)
library(rockchalk)
```

```{r, echo=T, message=F}
load("data_long.Rdata")
oxforddata <- read.csv("OxCGRT_latest.csv", header=TRUE)
```

To check whether country names are different in both datasets:
```{r, echo= T, results='hide'}
data_long$coded_country <- as.factor(data_long$coded_country)
oxforddata$CountryName <- as.factor(oxforddata$CountryName)

levels1 <- levels(data_long$coded_country)
levels2 <- levels(oxforddata$CountryName)

levels1<- as.data.frame(levels1)
levels2<- as.data.frame(levels2)

levels1$levels1 <-as.character(levels1$levels1)
levels2$levels2 <-as.character(levels2$levels2)

check <- comparedf(levels1, levels2, by.x="levels1", by.y="levels2")
summary(check)
```


Some data preparation
```{r rename countries, echo= T, results='hide'}
data_long$coded_country <- 
  plyr::revalue(data_long$coded_country , c("Hong Kong S.A.R."="Hong Kong", 
                                       "Kyrgyzstan" = "Kyrgyz Republic",
                                       "United Republic of Tanzania" = "Tanzania", 
                                       "United States of America" = "United States",
                                       "Republic of Serbia" = "Serbia",
                                       "Slovakia" = "Slovak Republic"))
```

Renaming and recoding variables:
```{r, echo= T, results='hide'}
data_long$age <- as.factor(data_long$age)
names(data_long)[names(data_long) == "age"] <- "Age"
names(data_long)[names(data_long) == "coded_country"] <- "Country"
names(data_long)[names(data_long) == "X"] <- "ID"
names(data_long)[names(data_long) == "RecordedDate"] <- "Date"
names(data_long)[names(data_long) == "gender"] <- "Gender"
names(data_long)[names(data_long) == "edu"] <- "Edu"
```

Recoding NA into zero's:
```{r, echo= T, results='hide'}
data_long$Close1[is.na(data_long$Close1)] <- 0
data_long$Close2[is.na(data_long$Close2)] <- 0
data_long$Close3[is.na(data_long$Close3)] <- 0
data_long$Close4[is.na(data_long$Close4)] <- 0
data_long$Close5[is.na(data_long$Close5)] <- 0
data_long$Close6[is.na(data_long$Close6)] <- 0
```

Delete participants with missing data on which country they currently live:
```{r, echo= T, results='hide'}
data_long$Country[data_long$Country == ""] <- NA

data_long <- data_long %>%
  filter(!is.na(Country))
```

Delete participants that are not citizens of the country they currently live in:
Note: Citizen = Have you been a citizen of this country since birth?
countryCitizen = Are you a citizen of this country?
```{r, echo= T, results='hide'}
data_long <- data_long %>%
  filter(countryCitizen == 1)
```

Delete participants with missing data on age
```{r}
data_long <-data_long %>%
filter(!is.na(Age))
```

Delete participants with missing data on gender
```{r}
data_long <-data_long %>%
filter(!is.na(Gender))
```

Recode gender into male = 0 and female = 1 and other = 2
```{r, echo = TRUE, results='hide'}
data_long$Gender[data_long$Gender == "2"] <- 0
```

Delete participants with missing data on education:
```{r, echo= T, results='hide'}
data_long <- data_long %>%
  filter(!is.na(Edu))
```

Delete emotion variables we don't study (Bored, Loved, Content, Excited)
```{r, echo=T, results='hide'}
data_long <- data_long %>%
  select(-c(Bored, Lov, Content, Exc))
```

Add number of measurements
```{r}
data_long$Date <- as.Date(data_long$Date)
data_long <- data_long %>% group_by(ID) %>% add_tally(wt = !is.na(Date))
```

Filter participants with at least 3 measurements
```{r}
data_long_min3 <- data_long %>% filter(n > 2)
```

Rename Wave column into Time ordered 1-12
```{r}
data_long_min3 <- data_long_min3 %>%
  rename(Time = Wave)

data_long_min3$Time <- data_long_min3$Time %>%
  plyr::revalue(c("w0"="1","w1"="2","w2"="3","w3"="4","w4"="5","w5"="6","w6"="7","w7"="8","w8"="9","w9"="10","w10"="11","w11"="12"))
```

```{r}
data_long_min3_g <- data_long_min3

save(data_long_min3_g, file="data_long_min3_g.Rdata")
```

Calculate number of participants per country & select countries with >20 participants:
```{r}
data_long_min3_g$Country <- as.factor(data_long_min3_g$Country)
data_long_min3_g <- as_tibble(data_long_min3_g)

Country_N <- data_long_min3_g %>%
  filter(Time == "1") %>%
  group_by(Country) %>%
  dplyr::summarise(N = n())
```

```{r}
data_long_min3_gn <- left_join(data_long_min3_g, Country_N, by="Country")
```

```{r}
data_long_min3_g20 <- data_long_min3_gn %>%
  filter(N>20)
```

```{r}
data_long_min3_g20 <- data_long_min3_g20 %>%
  select(-c(Citizen, countryCitizen))

summary(data_long_min3_g20)
summary(data_long_min3_g20$Country)
```

Save
```{r}
save(data_long_min3_g20, file="data_long_min3_g20.Rdata")
```

Recode oxford data:
```{r, echo= T, results='hide'}
oxforddata$Date <-anydate(oxforddata$Date)
oxforddata$Country <- oxforddata$CountryName
```

Drop not used variables:
```{r, echo= T, results='hide'}
Stringency_data <- oxforddata %>% select(Date, Country, StringencyIndex, ConfirmedCases, ConfirmedDeaths)
```

Impute Stringency Index, fill empty rows with last previously reported index score:
Create new Stringency Index variable first

```{r}
Stringency_data$StringencyIndex_imp <- Stringency_data$StringencyIndex
```

First join, then impute
```{r, echo= T, results='hide'}
data_long_min3_gstr <- left_join(data_long_min3_g20, Stringency_data, by=c("Country", "Date"))
```

Impute
```{r}
data_long_min3_gstr<-data_long_min3_gstr[with(data_long_min3_gstr, order(Country, Date)),]

data_long_min3_gstr2 <- data_long_min3_gstr %>%
  group_by(Country) %>%
  fill(StringencyIndex_imp, .direction = "down")

data_long_min3_gstr <- data_long_min3_gstr2
```

Check if StringencyIndex and StringencyIndex_imp are identical (they shouldnt be)
```{r}
identical(data_long_min3_gstr[["StringencyIndex"]],data_long_min3_gstr[["StringencyIndex_imp"]])
```

Save:
This dataset includes measurements from participants that (1) provided at least 3 measurements, (2) that are residents of the country they currently live in, (3) from countries with at least 20 participants, (4) provided data on age, and (5) with imputed Stringency index values, (6) for baseline through wave 11
```{r}
save(data_long_min3_gstr, file ="data_long_min3_gstr.Rdata")
```

Centering Stringency Index
```{r}
data_long_min3_gstrc <- gmc(data_long_min3_gstr, "StringencyIndex_imp", "Country", FUN = mean, suffix = c("_mn", "_dev"),
    fulldataframe = TRUE)
```

This dataset also adds the country mean centered stringency index 
```{r}
save(data_long_min3_gstrc, file="data_long_min3_gstrc.Rdata")
```

Make new age groups:
Youth: aged 18-24 coded as 1 <- 0
Young adults: aged 25-44 coded as 2 or 3 <- 1
Middle-aged adults: aged 45-64 coded as 4 or 5 <- 2
Older-aged adults: aged 65+ coded as 6, 7, or 8 <- 3

```{r}
data_long_min3_gstr_age <- data_long_min3_gstr 
data_long_min3_gstr_age$Age_new <- data_long_min3_gstr_age$Age
```

```{r}
data_long_min3_gstr_age$Age_new <- data_long_min3_gstr_age$Age_new %>%
  plyr::revalue(c("1"="0", "2"= "1", "3"="1", "4"="2", "5"="2", "6"="3", "7"="3", "8"="3"))
```

Create new variable that indicates sum of missings:
```{r, results='hide', message=F}
data_long_min3_gstr_age <- data_long_min3_gstr_age %>%
  group_by(ID, Time) %>%
mutate(Nmiss = sum(is.na(Ang)) + sum(is.na(Anxiety)) + sum(is.na(Nerv)) + sum(is.na(Depr)) + sum(is.na(Exh)) + 
               sum(is.na(Energ)) + sum(is.na(Insp)) + sum(is.na(Calm)) + sum(is.na(Rel))) %>%
  ungroup()
```

save
```{r}
save(data_long_min3_gstr_age, file="data_long_min3_gstr_age.Rdata")
```

```{r, results = "hide"}
data_means_g <- data_long_min3_gstr %>%
    dplyr::group_by(ID) %>%
    dplyr::summarise_each(funs(mean(., na.rm=TRUE)), 
                          Ang, Anxiety, Calm, Depr, Energ, Exh, Insp, Nerv, Rel)
```

```{r, results = "hide"}
save(data_means_g, file="data_means_g.Rdata")
```

Next = data imputation
