---
title: "Descriptive statistics including gender"
author: "Anne Margit"
date: "4/25/2021"
output: github_document
---

> Including all gender categories

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results = "hide"}
load("data_imputed_emomeans_maxweeksg.Rdata")
load("data_long_min3_gstr_age.Rdata")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)

```{r, message=F}
library(dplyr)
library(tidyverse)
library(stringr)
library(papaja)
library(ggpubr)
library(ggplot2)
library(stargazer)
```

# Missing data
```{r, results = "hide", message=F}
#Missing data
missing.values <- data_imputed_emomeans_maxweeksg %>%
  gather(key = "key", value = "val") %>%
  dplyr::mutate(is.missing = is.na(val)) %>%
  dplyr::group_by(key, is.missing) %>%
  dplyr::summarise(num.missing = n()) %>%
  dplyr::filter(is.missing==T) %>%
  dplyr::select(-is.missing) %>%
  dplyr::arrange(desc(num.missing))

```

```{r}
apa_table(missing.values, caption="Missing data")
```

# Participants
**Number of participants per country with original data**
```{r, results = "hide", message=F}
data_long_min3_gstr_age$Country <- as.factor(data_long_min3_gstr_age$Country)

Country_N <- data_long_min3_gstr_age %>%
  filter(Time == "1") %>%
  group_by(Country) %>%
  summarise(NCountry = n())
```

```{r}
apa_table(Country_N, caption = "Number of participants per country on baseline")
```

**Mean number of participants per country, SD, min and max**
```{r, results = "hide", message=F}
CountryN <- data_long_min3_gstr_age %>%
  group_by(Time, Country) %>%
  filter(Nmiss <9) %>%
  summarise(Ncountry = n_distinct(ID))

CountryNdistinct <- data_long_min3_gstr_age %>%
  group_by(Time) %>%
  filter(Nmiss <9) %>%
  summarise(Ncountry = n_distinct(Country))

CountryMean <- CountryN %>%
  group_by(Time) %>%
  summarise(MCountry = mean(Ncountry), SDCountry = sd(Ncountry)) %>%
  mutate(across(2:3, round, 2)) 
```

```{r}
CountryMean <- as.matrix(CountryMean)

stargazer(CountryMean,
type="html", df = TRUE, out="CountryMean.doc",  single.row=TRUE, digits = 2, flip = TRUE, align = TRUE)
```

```{r}
apa_table(CountryMean, caption = "Mean number of participants per country on baseline")
```

# Measurements

**Number of participants and measurements per wave with original data**
Create new variable that indicates sum of missings:
```{r, results='hide', message=F}
data_long_min3_gstr_age <- data_long_min3_gstr_age %>%
  group_by(ID, Time) %>%
mutate(Nmiss = sum(is.na(Ang)) + sum(is.na(Anxiety)) + sum(is.na(Nerv)) + sum(is.na(Depr)) + sum(is.na(Exh)) + 
               sum(is.na(Energ)) + sum(is.na(Insp)) + sum(is.na(Calm)) + sum(is.na(Rel))) %>%
  ungroup()
```

```{r, results = "hide", message=F}
data_long_min3_gstr_age$Time <- as.factor(data_long_min3_gstr_age$Time)

Wave_N_original <- data_long_min3_gstr_age %>% 
group_by(Time)%>%
summarise(NParticipants = n_distinct(ID[Nmiss<9]), NWave = sum (!is.na(Date)), NAng= sum(!is.na(Ang)), NAnx= sum(!is.na(Anxiety)), NNerv= sum(!is.na(Nerv)), NDepr= sum(!is.na(Depr)), NExh= sum(!is.na(Exh)), NEnerg= sum(!is.na(Energ)),  NInsp= sum(!is.na(Insp)), NCalm= sum(!is.na(Calm)), NRel= sum(!is.na(Rel)), NStr = sum(!is.na(StringencyIndex)))
```

```{r}
apa_table(Wave_N_original, caption="Number of measurements per wave original data")
```

```{r}
Wave_N_original <- as.matrix(Wave_N_original)

stargazer(Wave_N_original,
type="html", df = TRUE, out="Wave_N_original.doc",  single.row=TRUE, flip = TRUE, align = TRUE)
```

Mean number of assessments per participant
```{r}
pp_numbers <- data_long_min3_gstr_age  %>% 
 group_by(ID)%>%
  summarise(n_count = n_distinct(Date))

mean(pp_numbers$n_count)
sd(pp_numbers$n_count)
```

**Number of participants and measurements per wave with imputed data**
```{r, results = "hide", message=F}
data_imputed_emomeans_maxweeksg$Time <- as.factor(data_imputed_emomeans_maxweeksg$Time)

Wave_N_imp <- data_imputed_emomeans_maxweeksg %>% 
group_by(Time)%>%
summarise(NParticipants = n_distinct(ID[Nmiss<9]), NWave = sum (!is.na(Date)), NAng= sum(!is.na(Ang)), NAnx= sum(!is.na(Anxiety)), NNerv= sum(!is.na(Nerv)), NDepr= sum(!is.na(Depr)), NExh= sum(!is.na(Exh)), NEnerg= sum(!is.na(Energ)),  NInsp= sum(!is.na(Insp)), NCalm= sum(!is.na(Calm)), NRel= sum(!is.na(Rel)), NStr = sum(!is.na(StringencyIndex)))
```

```{r}
apa_table(Wave_N_imp, caption="Number of measurements per wave imputed data")
```

# Age
**Number of participants per age group on baseline**
```{r, results = "hide", message=F}
data_long_min3_gstr_age$Age <- as.factor(data_long_min3_gstr_age$Age)

Age_N <- data_long_min3_gstr_age %>%
  filter(Time=="1" & Nmiss <9) %>%
  group_by(Age) %>%
  summarise(NAge = n())
```

```{r}
apa_table(Age_N, caption="Number of participants per age group on baseline with original data")
```

**Number of participants per pooled age group**
```{r, results = "hide", message=F}
data_long_min3_gstr_age$Age_new <- as.factor(data_long_min3_gstr_age$Age_new)

Age_New <- data_long_min3_gstr_age %>%
  group_by(Time, Age_new) %>%
  filter(Nmiss <9) %>%
  summarise(NAge = n())
```

```{r}
apa_table(Age_New, caption="Number of participants per pooled age group on baseline with original data")
```

```{r}
Age_New <- as.matrix(Age_New)

stargazer(Age_New,
type="html", df = TRUE, out="Age_New.doc",  single.row=TRUE, digits = 2, align = TRUE)
```

**Number of males and females on baseline**  
```{r, results = "hide", message=F}
Gender_N <- data_long_min3_gstr_age %>%
  filter(Time == "1" & Nmiss <9) %>%
  group_by(Gender) %>%
  count(Gender)
```

```{r}
apa_table(Gender_N, caption="Number of males and females on baseline with original data", note= "Gender 0= male; 1= female")
```

**Number of males and females per wave with original data**     
```{r, results = "hide", message=F}
Gender_Wave <- data_long_min3_gstr_age %>%
  group_by(Time, Gender) %>%
    filter(Nmiss <9) %>%
  summarize(nGender = n_distinct(ID))
```

```{r}
apa_table(Gender_Wave, caption="Number of males and females per wave", note= "Gender 0= male; 1= female")
```

```{r}
Gender_Wave <- as.matrix(Gender_Wave)

stargazer(Gender_Wave,
type="html", df = TRUE, out="Gender_Wave.doc",  single.row=TRUE, digits = 2, flip = TRUE, align = TRUE)
```

**Number of males and females per pooled age group on baseline with original data**
```{r, results = "hide", message=F}
Age_New_Gender <- data_long_min3_gstr_age %>%
  filter(Time == "1") %>%
  select(Age_new, Gender) %>%
  group_by(Age_new, Gender) %>%
  count(Gender)
```
 
```{r}
apa_table(Age_New_Gender, caption = "Number of males and females per pooled age group on baseline",
          note= "Age 0= 18-24; 1= 25-44; 2= 45-64; 3= 65+, Gender 0= male; 1= female")
```

# StringencyIndex
**Mean and SD, minimum and maximum of Stringency Index and imputed Stringency Index per country**
```{r, results = "hide", message=F}
StringencySummary <- data_long_min3_gstr_age %>%
  group_by(Country)%>%
  summarize(Str_mean = mean(StringencyIndex, na.rm=TRUE), Str_SD = sd(StringencyIndex, na.rm=TRUE), 
            Str_max = max(StringencyIndex, na.rm=TRUE), Str_min = min(StringencyIndex, na.rm=TRUE),
            Str_imp_mean = mean(StringencyIndex_imp, na.rm=TRUE), Str_imp_SD = sd(StringencyIndex_imp, na.rm=TRUE), 
            Str_imp_max = max(StringencyIndex_imp, na.rm=TRUE), Str_imp_min = min(StringencyIndex_imp, na.rm=TRUE))
```

```{r}
apa_table(StringencySummary, caption="Stringency Index per country with original data")
```

**Mean and SD, minimum and maximum of Stringency Index per wave**
```{r, results = "hide", message=F}
StringencySummary2 <- data_long_min3_gstr_age %>%
  group_by(Time)%>%
  filter(Nmiss <9)%>%
  summarize(Str_mean = mean(StringencyIndex, na.rm=TRUE), Str_SD = sd(StringencyIndex, na.rm=TRUE), 
            Str_max = max(StringencyIndex, na.rm=TRUE), Str_min = min(StringencyIndex, na.rm=TRUE)) %>%
  mutate(across(2:5, round, 2))
```

```{r}
apa_table(StringencySummary2, caption="Stringency Index per wave with original data")
```

```{r}
StringencySummary2 <- as.matrix(StringencySummary2)

stargazer(StringencySummary2,
type="html", df = TRUE, out="StringencySummary2.doc",  single.row=TRUE, digits = 2, flip = TRUE, align = TRUE)
```


**Stringency Index violin plots**
```{r, results = "hide", message=F, warning=F}
data_imputed_emomeans_maxweeksg$Country <- as.character(data_imputed_emomeans_maxweeksg$Country)

data_graphs1 <- data_imputed_emomeans_maxweeksg %>%
filter(Country == "Argentina" |  Country == "Australia" | Country == "Brazil" | Country == "Canada" | Country == "Chile" | Country == "Croatia")

data_graphs2 <- data_imputed_emomeans_maxweeksg %>%
filter(Country == "France" | Country == "Germany" | Country == "Greece" | Country == "Hungary" | Country == "Indonesia" | Country == "Italy")

data_graphs3 <- data_imputed_emomeans_maxweeksg %>%
filter(Country == "Japan" | Country == "Kazakhstan" | Country == "Kosovo" | Country == "Malaysia" | Country == "Netherlands" | Country == "Peru")

data_graphs4 <- data_imputed_emomeans_maxweeksg %>%
filter(Country == "Philippines" | Country == "Poland" | Country == "Serbia" | Country == "Romania" | Country == "Russia" | Country == "Saudi Arabia")

data_graphs5 <- data_imputed_emomeans_maxweeksg %>%
filter(Country == "Singapore" | Country == "South Africa" | Country == "South Korea" | Country == "Spain" | Country == "Turkey" | Country == "Ukraine")

data_graphs6 <- data_imputed_emomeans_maxweeksg %>%
filter(Country == "United Kingdom" | Country == "United States" | Country == "Vietnam")


g_s1 <- ggplot(data_graphs1, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s2 <- ggplot(data_graphs2, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s3 <- ggplot(data_graphs3, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s4 <- ggplot(data_graphs4, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s5 <- ggplot(data_graphs5, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

g_s6 <- ggplot(data_graphs6, aes(StringencyIndex, Country)) + geom_violin(aes(fill=factor(Country)))

```

```{r, warning=F}
g_s1
g_s2
g_s3
g_s4
g_s5
g_s6
```

**Stringency Index over time per country**
```{r, results = "hide", message=F, warning=F}
g_s7 <- ggplot(data_graphs1, aes(x=Date, y=StringencyIndex)) + geom_line(aes(colour=factor(Country)), size=1) + 
  theme_minimal(base_size=10) +
  labs(title= "Severity of societal restrictions from March 2020 - July 2020", x="Date",
       y="Stringency Index") +
  theme(legend.position="bottom") +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust=0.5)) +
  expand_limits(y=c(20, 100)) +
  scale_x_continuous(labels=c("March", "April", "May", "June", "July"))

g_s8 <- ggplot(data_graphs2, aes(x=Date, y=StringencyIndex)) + geom_line(aes(colour=factor(Country)), size=1) + 
  theme_minimal(base_size=10) +
  labs(title= "Severity of societal restrictions from March 2020 - July 2020", x="Date",
       y="Stringency Index") +
  theme(legend.position="bottom") +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust=0.5)) +
  expand_limits(y=c(20, 100)) +
  scale_x_continuous(labels=c("March", "April", "May", "June", "July"))

g_s9 <- ggplot(data_graphs3, aes(x=Date, y=StringencyIndex)) +
  geom_line(aes(colour=factor(Country)), size=1) + 
  theme_minimal(base_size=10) +
  labs(title= "Severity of societal restrictions from March 2020 - July 2020", x="Date",
       y="Stringency Index") +
  theme(legend.position="bottom") +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust=0.5)) +
  scale_x_continuous(labels=c("March", "April", "May", "June", "July")) +
  expand_limits(y=c(20, 100))

g_s10 <- ggplot(data_graphs4, aes(x=Date, y=StringencyIndex)) + geom_line(aes(colour=factor(Country)), size=1) +
  theme_minimal(base_size=10) +
  labs(title= "Severity of societal restrictions from March 2020 - July 2020", x="Date",
       y="Stringency Index") +
  theme(legend.position="bottom") +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust=0.5)) +
  expand_limits(y=c(20, 100)) +
  scale_x_continuous(labels=c("March", "April", "May", "June", "July"))

g_s11 <- ggplot(data_graphs5, aes(x=Date, y=StringencyIndex)) +
  geom_line(aes(colour=factor(Country)), size=1) + 
  theme_minimal(base_size=10) +
  labs(title= "Severity of societal restrictions from March 2020 - July 2020", x="Date",
       y="Stringency Index") +
  theme(legend.position="bottom") +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust=0.5)) +
  expand_limits(y=c(20, 100)) +
  scale_x_continuous(labels=c("March", "April", "May", "June", "July"))

g_s12 <- ggplot(data_graphs6, aes(x=Date, y=StringencyIndex)) +
  geom_line(aes(colour=factor(Country)), size=1) + 
  theme_minimal(base_size=10) +
  labs(title= "Severity of societal restrictions from March 2020 - July 2020", x="Date",
       y="Stringency Index") +
  theme(legend.position="bottom") +
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust=0.5)) +
  expand_limits(y=c(20, 100)) +
  scale_x_continuous(labels=c("March", "April", "May", "June", "July"))
```
```{r, warning=F}
g_s7
g_s8
g_s9
g_s10
g_s11
g_s12
```

# Emotions 
**Mean, SD, and median of emotion factor scores**
```{r, results = "hide", message=F, warning =F}
emomeansN <- data_imputed_emomeans_maxweeksg %>%
  group_by(Time) %>%
  summarise(across(NAA:PAD, .fns=list(Mean = mean, SD = sd, Median = median), na.rm=TRUE,
                   .names="{col}_{fn}"))

emomeansN <- emomeansN %>%
  mutate(across(2:13, round, 2))
```

```{r}
apa_table(emomeansN, caption="Mean scores of emotion factor scores per wave")
```

```{r}
emomeansN <- as.matrix(emomeansN)

stargazer(emomeansN,
type="html", df = TRUE, out="emomeansN.doc",  single.row=TRUE, digits = 2, flip = TRUE, align = TRUE)
```


**Mean, SD, and median of emotion scores**
```{r, results = "hide", message=F, warning =F}
emorawmeansN <- data_imputed_emomeans_maxweeksg %>%
  group_by(Time) %>%
  summarise(across(Ang:Rel, .fns=list(Mean = mean, SD = sd, Median = median), na.rm=TRUE,
                   .names="{col}_{fn}"))
```

```{r}
apa_table(emorawmeansN, caption="Mean scores of emotion scores per wave")
```

**Boxplots of emotion factor scores across time**
```{r, results = "hide", message=F, warning=F}
theme_set(theme_classic())

gb_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(Age_new, NAA)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(Age_new, NAD)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_PAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(Age_new, PAA)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_PAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(Age_new, PAD)) + geom_boxplot(varwidth=T, aes(fill= Age_new)) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gb_NA <- ggarrange(gb_NAA, gb_NAD, ncol = 2, nrow = 1, common.legend= TRUE, legend = "bottom")

gb_PA <- ggarrange(gb_PAA, gb_PAD, ncol = 2, nrow = 1, common.legend= TRUE, legend = "bottom")
```

```{r, warning=F}
gb_NA
gb_PA
```

**Histograms of emotion factor scores**
```{r, results = "hide", message=F, warning=F}
g_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=NAA, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=NAD, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_PAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=PAA, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

g_PAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=PAD, fill=Age_new)) + geom_histogram(binwidth=1) + scale_fill_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+"))

gh_NA <- ggarrange(g_NAA, g_NAD, ncol = 2, nrow = 1, common.legend= TRUE, legend = "bottom")

gh_PA <- ggarrange(g_PAA, g_PAD, ncol = 2, nrow = 1, common.legend= TRUE, legend = "bottom")
```

```{r, warning=F}
gh_NA
gh_PA
```

# Negative affect high arousal
**Median NAA against week**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Median NAA against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=NAA))

plot_NAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Mean NAA against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=NAA, group = Age_new, color = Age_new))

plot_NAA + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean NAA against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=NAA))

plot_NAA + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + expand_limits(y=c(1, 5))
```

**Mean NAA against maximum stringency in weeks in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=NAA, group = Age_new, color = Age_new))

plot_NAA + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Negative affect low arousal
**Median NAD against week**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Median NAD against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=NAD))

plot_NAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
``` 

**Mean NAD against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=NAD, group = Age_new, color = Age_new))

plot_NAD + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean NAD against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=NAD))

plot_NAD + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + expand_limits(y=c(1, 5))
```

**Mean NAD against maximum stringency in weeks in different age groups**
```{r, echo=T, message=F, warning=F}
plot_NAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=NAD, group = Age_new, color = Age_new))

plot_NAD + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Positive affect high arousal
**Median PAA against week**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Median PAA against maximum stringency in weeks**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=PAA))

plot_PAA +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Mean PAA against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=PAA, group = Age_new, color = Age_new))

plot_PAA + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean PAA against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAA <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=PAA, group = Age_new, color = Age_new))

plot_PAA + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Positive affect low arousal
**Median PAD against week**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Median PAD against maximum stringency**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=PAD))

plot_PAD +  stat_summary(geom = "line", fun = median, size=1) + stat_summary(fun.data = median_hilow, 
                                                                    fun.args = (conf.int=.5)) + expand_limits(y=c(1, 5))
```

**Mean PAD against week in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=Week, y=PAD, group = Age_new, color = Age_new))

plot_PAD + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean PAD against maximum stringency in different age groups**
```{r, echo=T, message=F, warning=F}
plot_PAD <- ggplot(data_imputed_emomeans_maxweeksg, aes(x=WeeksMax, y=PAD, group = Age_new, color = Age_new))

plot_PAD + stat_summary(fun.y=mean, geom="line", size=1) + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

