---
title: "First analyses winning models"
author: "Anne Margit"
date: "12/03/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
options(scipen=999)
```

```{r, results = "hide"}
load("data_analyse1_fc.Rdata")
```

```{r, message=F}
library(dplyr)
library(tidyverse)
library(papaja)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom)
library(purrr)
library(stargazer)
```
**Negative affect high arousal**

```{r, message=F, comment=NA}
data_analyse1_fc <- data_analyse1_fc[with(data_analyse1_fc, order(Country, ID, Time)),]
data_analyse1_fc$Time <- as.numeric(data_analyse1_fc$Time)

model_NAA10 <- lme(fixed = NAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                   random = list (Country = pdDiag(~StringencyIndex_dev), ID = pdDiag(~StringencyIndex_dev)),
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAA10)
VarCorr(model_NAA10)
```
> Random ICs and slopes for country and ID, no correlation between ICS and slopes, AR structure

**Negative affect low arousal**
```{r, message=F, comment=NA}
data_analyse1_fc <- data_analyse1_fc[with(data_analyse1_fc, order(Country, ID, Time)),]
data_analyse1_fc$Time <- as.numeric(data_analyse1_fc$Time)

model_NAD10 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                   random = list (Country = pdDiag(~StringencyIndex_dev), ID = pdDiag(~StringencyIndex_dev)),
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAD10)
VarCorr(model_NAD10)
```

> This model has random slopes for Stringency at the ID and Country level, assumes no correlation between random slopes and intercepts, and assumes autoregressive correlation structure at the measurement level. 


**Positive affect high arousal**

```{r, message=F, comment=NA}
data_analyse1_fc <- data_analyse1_fc[with(data_analyse1_fc, order(Country, ID, Time)),]
data_analyse1_fc$Time <- as.numeric(data_analyse1_fc$Time)

model_PAA10 <- lme(fixed = PAA ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                   random = list (Country = pdDiag(~StringencyIndex_dev), ID = pdDiag(~StringencyIndex_dev)),
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PAA10)
VarCorr(model_PAA10)
```

> This model has random slopes for Stringency at the ID and Country level, assumes no correlation between random slopes and intercepts, and assumes autoregressive correlation structure at the measurement level. 


**Positive affect low arousal**
```{r, message=F, comment=NA}
data_analyse1_fc <- data_analyse1_fc[with(data_analyse1_fc, order(Country, ID, Time)),]
data_analyse1_fc$Time <- as.numeric(data_analyse1_fc$Time)

model_PAD10 <- lme(fixed = PAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                   random = list (Country = pdDiag(~StringencyIndex_dev), ID = pdDiag(~StringencyIndex_dev)),
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_PAD10)
VarCorr(model_PAD10)
```

> This model has random slopes for Stringency at the ID and Country level, assumes no correlation between random slopes and intercepts, and assumes autoregressive correlation structure at the measurement level. 


stargazer(model_NAA10, model_NAD10, model_PAA10, model_PAD10,
type="html",
out="star_NAA10.doc",  single.row=TRUE, digits = 2, align = TRUE, 
order = c("Intercept","SI", "Max SI (during)", "Max SI (after)", "SI x Max SI (during)", "SI x Max SI (after)"), 
covariate.labels = c("Intercept","SI", "Max SI (during)", "Max SI (after)", 
"SI x Max SI (during)", "SI x Max SI (after)"))







