---
title: "First analyses NAD including all gender categories"
author: "Anne Margit"
date: "4/25/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
```

```{r, results = "hide"}
load("data_analyse1_fcg.Rdata")

data_analyse1_fc <- data_analyse1_fcg
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A variable indicating the number of days before and after the day on which maximum stringency was reached for the respective country (DaysMax)
12. A variable indicating the number of weeks before and after the day on which maximum stringency was reached for the respective country (WeeksMax)
13. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr)
14. A dummy Str_dummy with 0 = before the peaj, 1 = during peak, 2 = after peak
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(papaja)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom)
library(purrr)
```

# Regression models

**Negative affect low arousal**

*Stringency Index x dummy interaction: random intercept for Country*
```{r, message=F, comment=NA}
model_NAD1 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                   random = ~1 | Country, 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD1)
```

*Stringency Index x dummy interaction: random intercept for ID*
```{r, message=F, comment=NA}
model_NAD2 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = ~1 | ID, 
                 data = data_analyse1_fc, 
                 na.action = na.omit,
                 control = list(maxIter = 100, opt = "optim"))

summary(model_NAD2)
```

> Bij NAD2 en NAD3 wilde hij niet convergen dus heb ik een max iteration toegevoegd

*Random intercept for Country and ID*
```{r, message=F, comment=NA}
model_NAD3 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = ~1 | Country/ID, 
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  control = list(maxIter = 100, opt = "optim"))

summary(model_NAD3)
```

*Random slope for Country*
```{r, message=F, comment=NA}
model_NAD4 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~StringencyIndex_dev, ID = ~1), 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD4)
```

*Random slope for ID*
```{r, message=F, comment=NA}
model_NAD5 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~1, ID = ~StringencyIndex_dev), 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD5)
```

*Random slope for Country and ID*
```{r, message=F, comment=NA}
model_NAD6 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = ~StringencyIndex_dev | Country/ID, 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD6)
```

*No correlation between intercept and slope for Country*
```{r, message=F, comment=NA}
model_NAD7 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list(Country = pdDiag(~StringencyIndex_dev), ID = ~StringencyIndex_dev), 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD7)
```

*No correlation between intercept and slope for ID*
```{r, message=F, comment=NA}
model_NAD8 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~StringencyIndex_dev, ID = pdDiag(~StringencyIndex_dev)), 
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD8)
```

*No correlation between intercept and slope for Country and ID*
```{r, message=F, comment=NA}
model_NAD9 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = pdDiag(~StringencyIndex_dev), ID = pdDiag(~StringencyIndex_dev)),
                  data = data_analyse1_fc, 
                  na.action = na.omit)

summary(model_NAD9)
```

*Autoregressive correlation structure*
```{r, message=F, comment=NA}
data_analyse1_fc <- data_analyse1_fc[with(data_analyse1_fc, order(Country, ID, Time)),]
data_analyse1_fc$Time <- as.numeric(data_analyse1_fc$Time)

model_NAD10 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                   random = list (Country = pdDiag(~StringencyIndex_dev), ID = pdDiag(~StringencyIndex_dev)),
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAD10)
```

*AR without random slope for country*
```{r, message=F, comment=NA}
model_NAD11 <- lme(fixed = NAD ~ StringencyIndex_dev + Str_dummy +  StringencyIndex_dev*Str_dummy,
                  random = list (Country = ~1, ID = pdDiag(~StringencyIndex_dev)), 
                  data = data_analyse1_fc, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAD11)
```

> Model NAD10 has the best fit (lowest BIC). This model has random slopes fo Stringency at the Country and ID level, assumes no correlation between random slope and intercept, and assumes autoregressive correlation structure at the measurement level. 

*QQ plot of residuals*
```{r, message=F, comment=NA}
par(mfrow = c(1,2))
lims <- c(-3.5,3.5)
hist(resid(model_NAD10, type = "normalized"),
freq = FALSE, xlim = lims, ylim =  c(0,.7),main = "Histogram of Standardized Residuals")
lines(density(scale(resid(model_NAD10))))
qqnorm(resid(model_NAD10, type = "normalized"),
xlim = lims, ylim = lims,main = "QQ plot")
abline(0,1, col = "red", lty = 2)
```

*Residuals vs fitted*
```{r, message=F, comment=NA}
plot(fitted(model_NAD10, level=2), residuals(model_NAD10, level=2), 
     main="residuals vs fitted at ID level")
abline(a=0, b=0,col="red")
plot(fitted(model_NAD10, level=1), residuals(model_NAD10, level=1), 
    main="residuals vs fitted at Country level")
abline(a=0, b=0,col="red")
```

*Plot random intercepts and slopes*
```{r, message=F, comment=NA}
plot(ranef(model_NAD10, level = 1))
plot(ranef(model_NAD10, level = 2))
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAD10)
```
*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAD <- effect("StringencyIndex_dev:Str_dummy", model_NAD10)

plot_NAD <- ggplot(as.data.frame(ef_NAD), 
       aes(StringencyIndex_dev, fit, color=Str_dummy)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_bw(base_size=12) + scale_color_discrete(name="Maximum stringency", labels = c("Before the peak", "During the peak", "After the peak")) + expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NAD
```

```{r, message=F, comment=NA}
coef_NAD = tidy(model_NAD10, 
               effects = "fixed")
```

*Effect sizes*
**Within person SD and average within person SD**
```{r, message=F, comment=NA}
load("ISDs_av.Rdata")
```

> Effect size = (regression coefficient * average ISD of X) / average ISD of Y) 

> For the intercept and the dummy variables (+ interaction) I only standardized Y, so the effect size = (regression coefficient / average ISD of Y)

```{r, message=F, comment=NA}
coef_NAD <- coef_NAD %>%
 left_join(., ISDs_av, by=c("term"="ind"))

coef_NAD <- coef_NAD %>%
  mutate(sd = ifelse(is.na(sd), 1, sd))

coef_NAD <- coef_NAD %>%
  mutate(sd = ifelse(row_number()== 5 | row_number()== 6, 6.12091, sd))

coef_NAD <- coef_NAD %>%
 mutate(e_size = (estimate * sd)/0.5319464)

coef_NAD <- coef_NAD %>%
  rename(isd = sd)
```

```{r}
coef_NAD
```



