---
title: "NAA final including gender_tables only"
author: "Anne Margit"
date: "05/09/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, set-options, echo=FALSE, cache= FALSE}
options(width=1000)
Sys.getenv('R_MAX_VSIZE')
options(scipen=999)
```

```{r, results = "hide"}
load("data_analyse2_p1.Rdata")
load("data_analyse2_p2.Rdata")
load("data_analyse2_p3.Rdata")

levels(data_analyse2_p1$Gender) <- c("M", "F", "O")
```

This dataset includes:

1. Data from all weekly measurement waves (baseline through wave 11, Time 1 through 12) 
2. Participants who provided at least 3 measurements 
3. Participants who are residents of the country they currently live in
4. Participants who provided info on age
5. Participants who provided info on gender (either male or female)
6. Data from countries with at least 20 participants
7. Pooled age groups
8. Imputed missing emotion scores
9. Combined emotion scores (NAA, NAD, PAA, PAD)
10. An imputed Stringency index (StringencyIndex_imp) 
11. A dummy Str_dummy with 0 = before the peak, 1 = during peak, 2 = after peak
12. A variable indicating the number of days before maximum stringency was reached (DaysMax_p1), during (DaysMax_p2), and after (DaysPhase3)
13.  A variable indicating the number of weeks before maximum stringency was reached (WeeksMax_p1), during (WeeksMax_p2), and after (WeeksPhase3)
14. A variable indicating the date on which maximum Stringency was reached for that country (DateMaxStr) and the max level reached (MaxStr) across the entire measurement period
15. A variable indicating the date on which minimum Stringency was reached for that country (DateMinStr) and the min level reached (MinStr) across the entire measurement period
15. Observations during which there was a second peak are excluded (N=583) 

> My comments are in block quotes such as this. 

```{r, message=F}
library(dplyr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(rockchalk)
library(effects)
library(nlme)
library(lattice)
library(broom.mixed)
library(purrr)
library(stargazer)
library("viridis")  
```

# Descriptives
**Number of participants per age group**

> 0 = 18-24, 1 = 25-44, 3= 45-64, 4= 65+

Phase 1
```{r, message=F, comment=NA}
data_analyse2_p1 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 2
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

Phase 3
```{r, message=F, comment=NA}
data_analyse2_p2 %>%
  group_by(Age_new) %>%
  summarise(NAge = n())
```

**Plots**
**Mean NAA against max stringency in WEEKS**
Phase 1 (only age differences)
```{r, echo=T, message=F, warning=F}
plot_NAA1 <- ggplot(data_analyse2_p1, aes(x=Age_new, y=NAA, fill= Age_new))

plot_NAA1 + geom_boxplot() +
   theme_minimal(base_size=12) +
   expand_limits(y=c(1, 5)) +
   theme(legend.position = "none") + 
   scale_x_discrete(labels= c("18-24", "25-44", "45-64", "65+")) +
   labs(title= "High-arousal negative affect", x = "Age", y="Mean NA") +
   theme(axis.title.y = element_text(vjust = 3), plot.title=element_text(hjust=0.5))  

  
plot_NAA1 + stat_summary(fun.y=mean, geom="line", size=1)  + 
   theme_minimal(base_size=12) + 
  geom_histogram(stat="summary", fun.data="mean_se", width=0.5) + 
  scale_color_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5)) +
  xlab("Age")
```

Phase 2
```{r, echo=T, message=F, warning=F}
plot_NAA2 <- ggplot(data_analyse2_p2, aes(x=WeeksMax_p2, y=NAA, group = Age_new, color = Age_new))

plot_NAA2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_NAA3 <- ggplot(data_analyse2_p3, aes(x=WeeksPhase3, y=NAA, group = Age_new, color = Age_new))

plot_NAA3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

**Mean NAA against max stringency in DAYS**
Phase 2
```{r, echo=T, message=F, warning=F}
plot_NAA2 <- ggplot(data_analyse2_p2, aes(x=DaysMax_p2, y=NAA, group = Age_new, color = Age_new))

plot_NAA2 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

Phase 3
```{r, echo=T, message=F, warning=F}
plot_NAA3 <- ggplot(data_analyse2_p3, aes(x=DaysPhase3, y=NAA, group = Age_new, color = Age_new))

plot_NAA3 + stat_summary(fun.y=mean, geom="line", size=1)  + geom_errorbar(stat="summary", fun.data="mean_se", width=0) + scale_colour_discrete(name = "Age", labels = c("18-24", "25-44", "45-64", "65+")) + expand_limits(y=c(1, 5))
```

# Phase 1
*Random: IC for ID and Country + Covariates Gender and Education*

> Edu: 0= Primary education, 1= General secondary education, 2= Vocational education, 3= Higher education, 4= Bachelors degree, 5= Masters degree, 6= PhD degree

```{r, message=F, comment=NA}
data_analyse2_p1$Edu <- as.numeric(data_analyse2_p1$Edu)

model_NAAp1 <- lme(fixed = NAA ~ Gender + Edu + Age_new,
                  random = ~1 | Country/ID, 
                  data = data_analyse2_p1, 
                  na.action = na.omit)

summary(model_NAAp1)
VarCorr(model_NAAp1)
```

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAAp1)
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAAp1 <- effect("Age_new", model_NAAp1)

plot_NAAp1 <- ggplot(as.data.frame(ef_NAAp1), 
  aes(Age_new, fit, color=Age_new)) + geom_line() + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + theme_minimal(base_size=12) + 
  labs(title="NAA during tightening of restrictions", y = "NAA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(name ="Age", labels=c("18-24", "25-44", "45-64", "65+")) +
  theme(legend.position = "none") +                 
  scale_color_discrete() + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NAAp1
```

*Effect sizes*
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p1 %>% 
  group_by(ID) %>%
  summarize_at(c("NAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("NAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect size = regression coefficient / average ISD of NAA

```{r, message=F, comment=NA}
coef_NAAp1 = broom.mixed::tidy(model_NAAp1, 
               effects = "fixed")

coef_NAAp1 <- coef_NAAp1 %>%
  mutate (e_size = estimate/0.4676462) %>% 
  mutate(across(3:8, round, 2)) 
         
```

```{r}
coef_NAAp1
coef_NAAp1 <- as.matrix(coef_NAAp1)
```

> The two oldest groups report lower NAA than the youngest group. Women report higher NAA compared to men. No difference between education levels. 

# Phase 2

*Best model*

> Random intercept for ID and Country, random slope for Country and ID, no correlation between random intercept and slope for Country, AR correlation structure at Measuement level

```{r, message=F, comment=NA}
data_analyse2_p2$Edu <- as.numeric(data_analyse2_p2$Edu)

data_analyse2_p2 <- data_analyse2_p2[with(data_analyse2_p2, order(Country, ID, Time)),]
data_analyse2_p2$Time <- as.numeric(data_analyse2_p2$Time)

model_NAAp2 <- lme(fixed = NAA ~ Gender + Edu + DaysMax_p2 + Age_new + DaysMax_p2*Age_new,
                  random = list(Country = pdDiag(~DaysMax_p2), ID = ~DaysMax_p2),  
                  data = data_analyse2_p2, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAAp2)
VarCorr(model_NAAp2)
```
*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAAp2, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAAp2 <- effect("DaysMax_p2:Age_new", model_NAAp2)

plot_NAAp2 <- ggplot(as.data.frame(ef_NAAp2), aes(DaysMax_p2, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=12) + 
  labs(title="A",
       x="Days", y = "High-arousal negative affect") +
  xlim(0,80)+
  theme(plot.title = element_text(size=12)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))

```

```{r, message=F}
plot_NAAp2
```

*Effect sizes*
**Within person SD and average within person SD**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p2 %>% 
  group_by(ID) %>%
  summarize_at(c("DaysMax_p2", "NAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("DaysMax_p2", "NAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age and covariates = regression coefficient / average ISD of NAA
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of NAA
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of NAA

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of NAA over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_NAAp2 = broom.mixed::tidy(model_NAAp2, 
               effects = "fixed")

coef_NAAp2 <- coef_NAAp2 %>%
  mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 4 |  row_number()== 6 |  row_number()== 7 |  row_number()== 8, estimate/0.4562862, (estimate*28)/0.4562862)) %>%
  mutate(across(3:7, round, 2)) 
          
```

```{r}
coef_NAAp2 <- as.matrix(coef_NAAp2)
coef_NAAp2
```

# Quadratic term
The interaction between age and daysmax was not significant (linear model) so these are dropped in the current model. The time variable needs to be centered at the midpoint (mean) to reduce collinearity between the linear and the quadratic components.

```{r, message=F, comment=NA}
data_analyse2_p2q <- gmc(data_analyse2_p2, "DaysMax_p2", "ID", FUN = mean, suffix = c("_mn", "_dev"),
    fulldataframe = TRUE)
```


```{r, message=F, comment=NA}
data_analyse2_p2q$Edu <- as.numeric(data_analyse2_p2q$Edu)

data_analyse2_p2q <- data_analyse2_p2q[with(data_analyse2_p2q, order(Country, ID, Time)),]
data_analyse2_p2q$Time <- as.numeric(data_analyse2_p2q$Time)

model_NAAp2q <- lme(fixed = NAA ~ Gender + Edu + DaysMax_p2_dev + Age_new  
                    + I(DaysMax_p2_dev^2) + I(DaysMax_p2_dev^2)*Age_new,
                  random = list(Country = pdDiag(~ DaysMax_p2_dev), 
                  ID = ~DaysMax_p2_dev),
                  data = data_analyse2_p2q, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAAp2q)
VarCorr(model_NAAp2q)

```

Results suggest that there is a decline of NAA over time. The quadratic effect was also significant and suggests an
decelerated decline in NAA over time, with no evidence of differences between age groups. 

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAAp2q, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAAp2q <- effect("Age_new:I(DaysMax_p2_dev^2)", model_NAAp2q)

plot_NAAp2q <- ggplot(as.data.frame(ef_NAAp2q), aes(DaysMax_p2_dev, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=10) + 
  labs(title="Quadratic NAA trajectories during peak restrictions",
       x="Days (centered)", y = "NAA") +
  theme(plot.title = element_text(hjust = 0.5, size=10)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))
```

```{r, message=F}
plot_NAAp2q
```


# Phase 3

```{r, message=F, comment=NA}
data_analyse2_p3$Edu <- as.numeric(data_analyse2_p3$Edu)

data_analyse2_p3 <- data_analyse2_p3[with(data_analyse2_p3, order(Country, ID, Time)),]
data_analyse2_p3$Time <- as.numeric(data_analyse2_p3$Time)

model_NAAp3 <- lme(fixed = NAA ~ Gender + Edu + DaysPhase3 + Age_new + DaysPhase3*Age_new,
                  random = list (Country = ~1, ID = ~DaysPhase3), 
                  data = data_analyse2_p3, 
                  na.action = na.omit,
                  correlation = corAR1(form = ~ Time | Country/ID))

summary(model_NAAp3)
VarCorr(model_NAAp3)
```

> Random intercept for ID and Country, random slope for ID and AR correlation structure at Measurement level

*Confidence intervals*
```{r, message=F, comment=NA}
intervals(model_NAAp3, which = 'fixed')
```

*Plot of predicted values*
```{r, results = "hide", message=F}
ef_NAAp3 <- effect("DaysPhase3:Age_new", model_NAAp3)

plot_NAAp3 <- ggplot(as.data.frame(ef_NAAp3), aes(DaysPhase3, fit, color=Age_new)) + 
  geom_line(size=1) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=1) + 
  theme_minimal(base_size=10) + 
  xlim(0,80)+
  labs(title="B",
       x="Days", y = "NAA") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_discrete(name="Age", labels = c("18-24", "25-44", "45-64", "65+")) + 
  expand_limits(y=c(1, 5))

```

```{r, message=F}
plot_NAAp3
```



```{r, message=F}
plot_NAAp2and3 <- ggarrange(plot_NAAp2, plot_NAAp3 , 
          ncol = 2, nrow = 1, common.legend=TRUE, legend= "bottom")

plot_NAAp2and3 <- annotate_figure(plot_NAAp2and3,top = text_grob("NAA trajectories during peak (A) and easing (B) of restrictions", size = 12))
  
  
```

```{r, message=F}
plot_NAAp2and3
  
```

*Effect sizes*
**Within person SD and average within person SD for NAA**
```{r, message=F, comment=NA}
ISDs <- data_analyse2_p3 %>% 
  group_by(ID) %>%
  summarize_at(c("NAA"), sd, na.rm=TRUE) %>%
  ungroup()

ISDs_av <- ISDs %>%
  summarize_at(c("NAA"), mean, na.rm=TRUE) %>%
  stack() %>%
  rename(sd=values) 
```

> Effect sizes for intercept and main effect of age = regression coefficient / average ISD of NAA
> Effect size for main effect of DaysMax = (regression coefficient * 28)/ average ISD of NAA
> Effect sizes for interaction effects = (regression coefficient * 28)/ average ISD of NAA

> The effect sizes for main effect of DaysMax and the interaction effects reflect the increase in SD of NAA over 4 weeks (28 days)

```{r, message=F, comment=NA}
coef_NAAp3 = broom.mixed::tidy(model_NAAp3, 
               effects = "fixed")

coef_NAAp3 <- coef_NAAp3 %>%
 mutate(e_size = ifelse(row_number()== 1 | row_number()== 2 |  row_number()== 3 |  row_number()== 4 |  row_number()== 6 |  row_number()== 7 |  row_number()== 8, estimate/0.421019, (estimate*28)/0.421019)) %>%
  mutate(across(3:7, round, 2)) 
```

```{r}
coef_NAAp3 <- as.matrix(coef_NAAp3)
coef_NAAp3
```

> Older people report lower NAA compared to younger people on the first day stringency reduces after the peak (main effect), there is no change over time in NAA for the youngest group, but the middle aged group (45-64) reports decreasing NAA over time (interaction effect). This trend is visible for the other age groups as well in the plot but not significant. 


```{r}
stargazer(coef_NAAp1, coef_NAAp2, coef_NAAp3,
type="html", df = TRUE, out="star_coefallphase_NAA.doc",  single.row=TRUE, digits = 3, align = TRUE)

stargazer(model_NAAp1, model_NAAp2, model_NAAp2q, model_NAAp3,
type="html", df = TRUE, out="starallphasesNAA.doc",  single.row=TRUE, digits = 3, align = TRUE,
intercept.top = TRUE, intercept.bottom = FALSE)

```


